Jordan Deyton: -- ADDRESSED! --

1 - abstract - "feedback driven way w*h*ere solutions"
1 - keywords didn't render correctly?
3 - 2.0.1. (1st paragraph) - "Those same computational scientist*s*"
4 - Executing jobs (1st paragraph) - "remotely remotely"
4 - Analyzing results (1st paragraph) - "in preparation for follow*ing* simulations"
5 - 3.1 (second paragraph) - "since it often changes *at* run time"
6 - (second paragraph) - "section ??"
6 - (just before last paragraph) - the caption for table 1 is shown here
7 - 3.1.2 (1st paragraph) - "By conventional"
8 - 3.2 (2nd paragraph) - "ICE originally *?* a significant amount"
10 - 4.3 (1st paragraph) - "an ICE-based workbench for perform*ing* simulations"
13 - (3rd paragraph) - "Other tools create*d* with ICE"
13 - (3rd paragraph) - "was a*s* simple as"
14 - 7 - "and described how its has been"

Dasha Gorin: -- ADDRESSED! --

Abstract:
"Computational scientists typically interact with simulation software in a feedback driven way where solutions and workflows are developed iteratively and simultaneously." 

Also on page 11, section 4.5 "Quantum Computing":
As quantum computing grows, so too does the need for sophisticated software...

Bottom of page 13:
"Interested parties may inquire by contacting the corresponding author or visiting the website."

Greg Watson (in addition to other comments):

Here are a couple of additonal typos I found:
p5, last para, "The list of available workflow*s* that can be..."
p8 1st para "... create workflows through wiring diagram*s*."

Hari:

I hope you are doing well! Overall the paper looks good. Thanks for including me on it!

For grammar: I would just read through the text to correct some minor spelling and grammar issues. Minor stuff like the following sentence: "ICE originally a significant amount of visualization support"

For the story: Are you planning a general software infrastructure paper? 

The highlights and use cases make a solid argument, but the tone of the paper comes off a little reserved.

For instance,  "The impact of software tools such as ICE are hard to quantify. However, there are several places where ICE has significantly assisted its development team and others."

I personally like being realistic and a bit humble that ICE isn't being touted as the best thing since sliced bread without enough proven track record, which a lot of software papers tend to do. 

At the same time this strategy might have the opposite effect where reviewers don't think it's good enough because the authors aren't excited about their work. Maybe rewriting this or moving it later or to end of the section would be prudent. Then the text would suggest: "Look at the cool and useful stuff ICE is already capable of, but this is just the beginning and ICE has an exciting future ahead of it"